Figure 2 and figure 2 supplementary material

### 2022-03-10 Figures/Figure2.Rmd
fix Figure2 corrplot mean with NANs

    order <- store_corrs %>% 
      group_by(measure2) %>%
      dplyr::summarize(r = mean(r)) %>% 
      arrange(desc(r)) %>% 
      mutate(measure1 = "Average",
             p = NA,
             sig_p = TRUE,
             p_if_sig = NA,
             r_if_sig = r ) %>%
      dplyr::relocate(measure1, .before = measure2)

>>>>

    order <- store_corrs %>% 
      drop_na(r) %>% # Epidish_CBSX_LM22 dont work for UVM in Neutrophils and mean dont work with NANs
      group_by(measure2) %>%
      dplyr::summarize(r = mean(r)) %>% 
      arrange(desc(r)) %>% 
      mutate(measure1 = "Average",
             p = NA,
             sig_p = TRUE,
             p_if_sig = NA,
             r_if_sig = r ) %>%
      dplyr::relocate(measure1, .before = measure2)
